Risk Perceptions for Wearable Devices

### 2016-01-29 USEC2016-camera-ready/camera-ready.tex
camera ready version with template

\documentclass{sig-alternate-hotpets15}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}

\def\etal{{\it et al.~}}
\newenvironment{packed_enum}{
\begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{enumerate}}
\newenvironment{packed_item}{
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}}

\begin{document}
\title{Risk Perceptions for Wearable Devices}
\numberofauthors{1}
\author{
 \alignauthor Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,3}, Joong Hwa Lee\textsuperscript{2}, David Wagner\textsuperscript{1}\\
   \vspace{0.5em}
   \affaddr{\textsuperscript{1}University of California, Berkeley, \{lnl,egelman,daw\}@cs.berkeley.edu}, \textsuperscript{2}dlwndghk94@berkeley.edu\\
   \affaddr{\textsuperscript{3}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
}

\maketitle

\begin{abstract}
\indent\indent Wearable devices, or ``wearables,'' bring great benefits but also potential risks that could expose users' activities without their awareness or consent. We surveyed 1,782 Internet users about risks associated with the capabilities of popular wearable devices on the market in order to identify risks that users find concerning. Our study relatively ranks a range of potential data capture scenarios enabled by wearable devices, investigates the impact of the recipient of the data on the perceived risk of data capture, and explores the landscape of users' concerns associated with wearable devices (including privacy and security, but also including factors such as increased safety risk, changes in social behaviors, and how wearable devices are unfashionable). To our knowledge, this is the largest user-based experiment concerning security and privacy concerns regarding wearables. We hope that this work will inform the community about user perceptions of wearable devices and aid in the design of future user notification, permission management, and access control schemes for wearables.
\end{abstract}

% A category with the (minimum) three required fields
%\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]

%\terms{Human Factors}{Measurement}{Security}

\keywords{Privacy, Security, User Studies, Risk Perception, Ubiquitous Computing, Wearable Devices} % NOT required for Proceedings

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{images/prompt.png}
	\caption{An example of a wearable scenario question participants saw while taking the survey.}
	\label{fig:prompt}
\end{figure}

@@

Felt \etal previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}. Their survey asked 3,115 smartphone users about 99 risk scenarios. Participants were asked how upset they would be if a certain action occurred without their permission. Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).'' Our methodology closely follows that study, but with scenarios chosen to shed light on the security and privacy risks of wearable devices.\\

@@

\end{document}

>>>>

%% Modified for USEC 2016 on 2015/10/06

\documentclass[conference]{IEEEtran}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}
\pagestyle{plain}

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Risk Perceptions for Wearable Devices}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Linda Lee, JoongHwa Lee, Serge Egelman, David Wagner}
\IEEEauthorblockA{University of California, Berkeley\\
\{lnl@,dlwndghk94,egelman,daw\}@cs.berkeley.edu}}
%\and
%\IEEEauthorblockN{JoongHwa Lee}
%\IEEEauthorblockA{University of California, Berkeley\\
%dlwndghk94@berkeley.edu }
%\and
%\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
%\IEEEauthorblockA{Starfleet Academy\\
%someemail@somedomain.com}}

\IEEEoverridecommandlockouts
\makeatletter\def\@IEEEpubidpullup{9\baselineskip}\makeatother
\IEEEpubid{\parbox{\columnwidth}{Permission to freely reproduce all or part
    of this paper for noncommercial purposes is granted provided that
    copies bear this notice and the full citation on the first
    page. Reproduction for commercial purposes is strictly prohibited
    without the prior written consent of the Internet Society, the
    first-named author (for reproduction of an entire paper only), and
    the author's employer if the paper was prepared within the scope
    of employment.  \\
    USEC '16, 21 February 2016, San Diego, CA, USA\\
    Copyright 2016 Internet Society, ISBN 1-891562-42-8\\
    http://dx.doi.org/10.14722/usec.2016.23006
}
\hspace{\columnsep}\makebox[\columnwidth]{}}

% make the title area
\maketitle

\begin{abstract}
\noindent Wearable devices, or ``wearables,'' bring great benefits but also potential risks that could expose users' activities without their awareness or consent. We surveyed 1,782 Internet users about risks associated with the capabilities of popular wearable devices on the market in order to identify risks that users find concerning. Our study relatively ranks a range of potential data capture scenarios enabled by wearable devices, investigates the impact of the recipient of the data on the perceived risk of data capture, and explores the landscape of users' concerns associated with wearable devices (including privacy and security, but also including factors such as increased safety risk, changes in social behaviors, and how wearable devices are unfashionable). To our knowledge, this is the largest user-based experiment concerning security and privacy concerns regarding wearables. We hope that this work will inform the community about user perceptions of wearable devices and aid in the design of future user notification, permission management, and access control schemes for wearables.
\end{abstract}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{prompt.png}
	\caption{An example of a wearable scenario question participants saw while taking the survey.}
	\label{fig:prompt}
\end{figure}

@@

Felt {\it et al.} previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}. Their survey asked 3,115 smartphone users about 99 risk scenarios. Participants were asked how upset they would be if a certain action occurred without their permission. Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).'' Our methodology closely follows that study, but with scenarios chosen to shed light on the security and privacy risks of wearable devices.\\

@@

% that's all folks
\end{document}
